---
title: "Equivalent_data_selection"
author: "Fabienne Lind"
date: "2023-02-12"
output: html_document
---

# Automated Article Selection and Validation

### Data and case description

In this tasks, we will create and validate search strings for different languages and cases.
I pre-selected data in three language for multiple outlets by using a very broad search string: 

en: "climate"
de: "klima"
fr: "climatique"

Such a broadly defined search string allows to validate a more specific search string. 
Let's load the data first and take a look. Each row represents one news article.

```{r}

#articles <- meta_articles_all
articles <- read.csv("https://raw.githubusercontent.com/fabiennelind/Workshop_Multilingual-Text-Analysis_and_Comparative-Research/master/data/climate_news.csv")

```

## Task1: Warm-up

The data includes data for several countries. Select at least two subsets according to your comparative research question and store the result in seperate dataframes.

```{r}


```


## Task 2: Automated Data Selection with a Search String per Language

From our universe of articles (all mentioning climate) we like to select only those articles that address climate activism. We intend to measure the salience of climate activism per article as simple binary variable:
1 = Climate activism is mentioned
0 = No climate activism is mentioned.



### Task2a: Concept Definition

 As a first step, we define the concept more closely

**Climate activism** is here defined as XXX 


### Task2b Search string creation

Define several keywords per search string.


```{r}

```


### Task2c Text Preprocessing

Before we search the keyword in the text, check if you need to preprocess the text.

```{r}


```

### Task2d Text Classification

The next task is to search the keywords in the article texts and to create a new column of the `articles` dataframe  




## Outlook

We have now managed to get an automated measurement for the variable. **But how valid is this measurement?** Does our small set of keyword represent the concept adequately?

A common procedure in automated content analysis is to test construct validity. We ask:
How close is this automated measurement to a more trusted measurement: Human understanding of text.

We will see how this can be put into practice when we discuss output evaluation later on. 



