---
title: "Implementing input alignment via machine translation"
author: "Fabienne Lind"
date: "October, 2022"
output:
  html_document:
    df_print: paged
---

# Implementing input alignment via machine translation

## Data

For the next tasks, we will work with an example text data, headlines from news articles about migration. The data set is a subset of the [REMINDER media corpus](https://doi.org/10.11587/IEGQ1B).

Let's load the data first and take a look. Each row represents one news article. How many articles per country do we have?

```{r}

articles <- read.csv("https://raw.githubusercontent.com/fabiennelind/Workshop_Multilingual-Text-Analysis_and_Comparative-Research/master/data/multilingual_data_annotated.csv")

#as.data.frame(articles)
table(articles$country) 

```

## Tasks:

1. Count the number of characters for the German and Spanish part of the corpus and calculate the prize for full text translation with the DeepL API. 
How expensive is it to translate the German and Spanish headlines into English? (with the DeepL API 1 Mil. characters cost 20 euros)

2. DeepL offers also the [DeepL API Free](https://www.deepl.com/en/docs-api/) which allows a maximum of 500,000 characters/month to be translated for free. To use the API, it is necessary to create an account and provide your credit card details. After creating an account you will receive an Authentication Key (You find it your DeepL account settings). With [deeplr](https://github.com/zumbov2/deeplr) [(Zumbach & Bauer, 2021)](https://CRAN.R-project.org/package=deeplr), a new wrapper for the DeepL API it is easily possible to work with it from R. 

If you feel comfortable with providing your credit card details, set up a DeepL API Free account and translate the Spanish and German headlines into English with the deeplr package. Save the translated version in a column called `headline_mt`.


Just in case, with the following command you can just read in the translated headlines for you to move on to the next task (in case the translation did not work).

```{r}

#articles <- read.csv("https://raw.githubusercontent.com/fabiennelind/Workshop_Multilingual-Text-Analysis_and_Comparative-Research/master/data/multilingua#l_data_annotated_translated.csv")

```

3. Use the R package UDPipe to lemmatize the English headlines. The goal is to have a new column in you data frame that includes the lemmatized text.

